% Upper-case    A B C D E F G H I J K L M N O P Q R S T U V W X Y Z
% Lower-case    a b c d e f g h i j k l m n o p q r s t u v w x y z
% Digits        0 1 2 3 4 5 6 7 8 9
% Exclamation   !           Double quote "          Hash (number) #
% Dollar        $           Percent      %          Ampersand     &
% Acute accent  '           Left paren   (          Right paren   )
% Asterisk      *           Plus         +          Comma         ,
% Minus         -           Point        .          Solidus       /
% Colon         :           Semicolon    ;          Less than     <
% Equals        =           Greater than >          Question mark ?
% At            @           Left bracket [          Backslash     \
% Right bracket ]           Circumflex   ^          Underscore    _
% Grave accent  `           Left brace   {          Vertical bar  |
% Right brace   }           Tilde        ~

%
% NSF Biographical Sketch: Dr. Theodore P. Pavlic
%
% Copyright (c) 2013 by Theodore P. Pavlic
% All rights reserved.
%

\documentclass[svgnames,11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{times}
\renewcommand\thesection{(\alph{section})}
\renewcommand\thesubsection{(\alph{subsection})}

\usepackage{calc}

\usepackage{lastpage}
%\newcommand{\pageoflastpage}{Page {\thepage} of \pageref*{LastPage}}
%\newcommand{\pageoflastpage}{{\thepage} of \pageref*{LastPage}}
\newcommand{\pageoflastpage}{}

% Redefine the plain pagestyle for the title page
\makeatletter
\let\oldps@plain\ps@plain
\renewcommand{\ps@plain}{\oldps@plain%
\renewcommand{\@evenfoot}{\hfil\pageoflastpage\hfil}%
\renewcommand{\@oddfoot}{\@evenfoot}}
\makeatother

% Use fancy for non-title pages
\usepackage{fancyhdr}
\fancyhead{}
\fancyfoot{}
\cfoot{\pageoflastpage}
\pagestyle{fancy}

\usepackage{xspace}

\usepackage[shortlabels]{enumitem}
\usepackage{graphicx}
\usepackage{varioref}
\usepackage[%
        colorlinks=true,urlcolor=,
        pdfpagelabels=true,hypertexnames=true,
        plainpages=false,naturalnames=true,
        ]{hyperref}
%
\usepackage{url}
\newcommand\doilink[1]{\href{http://dx.doi.org/#1}{#1}}
\newcommand\doi[1]{doi:\doilink{#1}}

\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{1em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newlist{bibsection}{itemize}{3}
\setlist[bibsection]{label=,leftmargin={\bibhang+\widthof{[9]}},%
        itemindent=-\bibhang,
        itemsep=\bibsep,parsep=\z@,partopsep=0pt,
        topsep=0pt}
\newlist{bibenum}{enumerate}{3}
\setlist[bibenum]{label=\textbf{\arabic*.},leftmargin={\bibhang+\widthof{[999]}},%
        itemindent=-\bibhang,
        itemsep=\bibsep,parsep=\z@,partopsep=0pt,
        topsep=0pt}
\let\oldendbibenum\endbibenum
\def\endbibenum{\oldendbibenum\vspace{-.6\baselineskip}}
\let\oldendbibsection\endbibsection
\def\endbibsection{\oldendbibsection\vspace{-.6\baselineskip}}
\makeatother

\title{%
        \vspace{-2\baselineskip}
            \normalsize
            Biographical Sketch\\
            {\large\textbf{Dr.~Josef C.~Uyeda}}\\
            \vspace{0.5\baselineskip}
            \hrule
            \vspace{0.5\baselineskip}
            Department of Biological Sciences, University of Idaho,
            e-mail: \href{mailto:josef.uyeda@gmail.com}{josef.uyeda@gmail.com},
            tel: +1-503-559-6433
        \vspace{-1.5ex}
        }
\date{}
\author{}

\hypersetup{%
        pdfsubject={NSF Biographical Sketch of Dr.~Josef C.~Uyeda},
        pdfauthor={Dr. Theodore P.~Pavlic},
        pdftitle={NSF Biographical Sketch of Dr.~Josef C.~Uyeda},
        pdfkeywords={}
        }

\newcommand{\ie}{i.e.\xspace}
\newcommand{\eg}{e.g.\xspace}

\begin{document}

\maketitle
\vspace{-4\baselineskip}

\subsection{Professional Preparation}

    Willamette University, Salem, OR;
        Biology; \textit{summa cum laude}
        B.A. with honors, 2006
        \\
    Oregon State University, Corvallis, OR;
        Zoology;
        Ph.D., 2012
        \\
    University of Idaho, Moscow, ID;
        Institute for Bioinformatics and Evolutionary Studies (IBEST);
        Postdoctoral Fellow, 2012--present

\subsection{Appointments}

\begin{itemize}[label={\quad 9999--9999:},leftmargin=*,itemsep=0pt]

    \item[2012--present:]
        \textbf{Postdoctoral Fellow},
        University of Idaho,
        Moscow, ID
\end{itemize}

\subsection{Products}

\begin{bibenum}[itemsep=5pt]

    \item \textbf{Pavlic, T.P.}, S.~Wilson, G.P.~Kumar, and S.~Berman.
        An enzyme-inspired approach to stochastic allocation of robotic
        swarms around boundaries. In: \emph{Proceedings of the 16th
        International Symposium on Robotics Research},
        December 16--19. 2013. Accepted.

    \item \textbf{Pavlic, T.P.}, and K.M.~Passino. Distributed and
        cooperative task processing: Cournot oligopolies on a graph.
        \emph{IEEE Transactions on Cybernetics}. 2013. In press.
        \doi{10.1109/TCYB.2013.2271776}

    \item Kumar, G.P., A.~Buffin, \textbf{T.P.~Pavlic}, S.C.~Pratt, and
        S.M.~Berman. A stochastic hybrid system model of collective
        transport in the desert ant \emph{Aphaenogaster cockerelli}. In:
        \emph{Proceedings of the 16th International Conference on Hybrid
        Systems: Communication and Control}, April 8--11,
        2013.

    \item \textbf{Pavlic, T.P.} Physical Stigmergy for decentralized
        constrained optimization: an intelligent lighting example. In:
        \emph{Proceedings of the 4th International Conference on
        Cyber-Physical Systems}, April 8--11, 2013.
        Poster abstract.

    \item \textbf{Pavlic, T.P.}, S.~P.~Peddi, P.A.G.~Sivilotti, and B.W.~Weide.
        Getting Out of the Way--Safety Verification without Compromise.
        In: \emph{Proceedings of the 2012 IEEE/ACM Third International
        Conference on Cyber-Physical Systems}, April
        17--19, 2012. Poster abstract.

    \item \textbf{Pavlic, T.P.}, and K.M.~Passino. Generalizing foraging theory
        for analysis and design. \emph{The International Journal of
        Robotics Research [Special Issue on Stochasticity in Robotics
        and Bio-Systems Part 1]}. 30(5):505--523. 2011.
        \doi{10.1177/0278364910396551}

    \item \textbf{Pavlic, T.P.}, and K.M.~Passino. The sunk-cost effect as an
        optimal rate-maximizing behavior. \emph{Acta Biotheoretica},
        59(1):53--66. 2011. \doi{10.1007/s10441-010-9107-8}

    \item \textbf{Pavlic, T.P.}, and K.M.~Passino. When rate maximization is
        impulsive. \emph{Behavioral Ecology and Sociobiology},
        64(8):1255--1265. August 2010. \doi{10.1007/s00265-010-0940-1}

    \item \textbf{Pavlic, T.P.}, and K.M.~Passino. Foraging theory for
        autonomous vehicle speed choice. \emph{Engineering Applications
        of Artificial Intelligence}, 22:482--489, April 2009.
        \doi{10.1016/j.engappai.2008.10.017}

    \item Freuler, R.J., M.J.~Hoffmann, \textbf{T.P.~Pavlic}, J.M.~Beams,
        J.P.~Radigan, P.K.~Dutta, J.T.~Demel, and E.D.~Justen.
        Experiences with a Comprehensive Freshman Hands-On Course~--
        Designing, Building, and Testing Small Autonomous Robots. In:
        \emph{Proceedings of the 2003 American Society for Engineering
        Education Annual Conference \& Exposition}, 2003.

\end{bibenum}

\subsection{Synergistic Activities}

\begin{bibenum}[itemsep=4pt]

    \item \textbf{Conference service:}
        (i) Organizer and associate editor for invited session:
        ``Correctness by Verification and Design'',
        14\textsuperscript{th} IEEE Conference on Intelligent
        Transportation Systems, Washington, DC, October
        5--7, 2011.
        (ii) Organizer for proposed mini-symposium: ``Optimization and
        Rationality in Eusocial Insects'', 2013 Society for Mathematical
        Biology Annual Meeting and Conference, Tempe, AZ,
        June 10--13, 2013
        (iii) Co-organizer for technical session: ``Complex Systems of
        Social Insects in Research and Education'', 2013 Biomathematics
        and Ecology: Education and Research, Arlington, VA,
        October 11--13, 2013.

    \item \textbf{University service:} Chair of committee for the
        development of biomimicry and bio-inspired research and education
        initiatives at Arizona State University, 2013.

    \item \textbf{Community service:}
        (i) As NSF GK-12 fellow, developed and implemented science
        lessons for local inner-city public school, 2006--2007.
        (ii) Recognized in \emph{Wired} magazine for OSS work Linux
        Virtual Server project, 2000.

    \item \textbf{Mentoring:}
        (i) Founding faculty co-adviser for Interdisciplinary Complexity
        Science Student Organization at Arizona State University, 2013.
        (ii) Founding mentor of 2002 FIRST high-school robotics team
        that received regional honor for inspiration in engineering,
        Dublin, OH.
        (iii) Founding mentor of 2001 FIRST LEGO League all-girls
        middle-school robotics team, Columbus, OH

    \item \textbf{Teaching:}
        (i) Authored hundreds of pages of Creative-Commons-licensed
        course material for courses in analog electronics and control
        for undergraduate and graduate students, The Ohio State
        University, 2007--2009.
        (ii) Developed and implemented Electrical and Computer
        Engineering undergraduate student design project on
        retrofittable vehicle-to-vehicle communications system for
        adaptive cruise control in mixed-traffic environments, The Ohio
        State University, 2012.
        (iii) Mathematical modeling guest lecturer, Research Strategies
        for Animal Behavior, Arizona State University, 2013.

\end{bibenum}

\subsection{Collaborators \& Other Affiliations}

\begin{bibsection}

    \item \textbf{Collaborators and Co-Editors:}
        \emph{The Ohio State University}:
            Manas Agrawal;
            Emrah Adamey;
            Vijay Gadepally;
            Arda Kurt;
            Ashok K.~Krishnamurthy;
            \"{U}mit \"{O}zg\"{u}ner;
            Jaeyong Park;
            Kevin M.~Passino;
            Sai Prathyusha Peddi;
            Keith A.~Redmill;
            Paolo A.~G.~Sivilotti;
            Michael Vernier;
            Alan D.~Weide;
            Bruce W.~Weide;
        \emph{Arizona State University}:
            Dieter Armbruster;
            Spring Berman;
            Aur{\'{e}}lie Buffin;
            Hinsby Cadillo-Quiroz;
            Luis Cisneros;
            Paul Davies;
            Jessica D.~Ebie;
            James J.~Elser;
            Georgios E.~Fainekos;
            Jennifer Fewell;
            Jon F.~Harrison;
            Christal Johnson;
            Yun Kang;
            Yang Kuang;
            Ganesh P.~Kumar;
            Alex Nachman;
            Susan Neuer;
            Stephen C.~Pratt;
            Hana Putnam;
            Jason Raymond;
            P.~Logan Rogers;
            Takao Sasaki;
            Zachary Shaffer;
            Oyita Udiani;
            Taylor Vance;
            Sara Imari Walker;
            Sean Wilson;
        \emph{New Jersey Institute of Technology}:
            Simon Garnier;
            Chris Reid

    \item \textbf{Graduate Advisers and Postdoctoral Sponsors:}
        \emph{The Ohio State University}:
            Kevin M.~Passino;
            Paolo A.~G.~Sivilotti;
        \emph{Arizona State University}:
            Stephen C.~Pratt (Arizona State University)

    \item \textbf{Thesis Adviser and Postgraduate-Scholar Sponsor:}
        \emph{Undergraduate honors thesis students:}
            Christal Johnson (Arizona State University).
        Total graduate students: 0; Total postgraduate scholars: 0.


\end{bibsection}

\end{document}
