---
title: "The evolution of energetic scaling across the vertebrate tree of life"
output: html_notebook
---

This is an R markdown workbook that provides a guide to the analyses conducted in Uyeda et al. 2017; "The evolution of energetic scaling across the vertebrate tree of life". 

#### Load Required Packages
```{r}
library(treeplyr)
devtools::install_github("uyedaj/bayou", ref="dev")
library(bayou)
library(rotl)
library(phytools)
library(Matrix)
library(phylolm)
source("BMRstudyFunctions.R")
setwd("~/repos/bmr/R/")
```


# Data Preparation

```{r}

## Read in the dataset
allwhite <- read.csv("../datasets/all_white_etal.csv")
## Boltzmann's constant & temperature to estimate metabolic rate at using Arrhenius equation
k <- 8.617332478E-5
T2 <- 293.15

allwhite <- mutate(allwhite, lnBMR = log(MR), lnMass = log(mass), iTemp = 1/k*1/(temp+273.15))

## Fit a multiple regression model to estimate the average Ei value across species
tmp <- filter(allwhite, !is.na(mass), !is.na(temp), !is.na(MR))
mod1 <- lm(lnBMR ~ lnMass + iTemp + species, data=tmp)
Ei <- mod1$coef[3]

## Some data don't have raw masses, only mean mass. Here we take the log of the means as an estimate of the mean of the logs.
allwhite[which(is.na(allwhite[,2])),'mass'] <- sapply(allwhite[which(is.na(allwhite[,2])),1], function(x) mean(allwhite$mean.mass[which(allwhite$species==x)], na.rm=TRUE))

allwhite <- filter(allwhite, !is.na(mass), !is.na(temp), !is.na(MR)) %>%  mutate(., lnBMR = log(MR), lnMass = log(mass), iTemp = 1/k*1/(temp+T2))

new.dat <- group_by(allwhite, species) %>% summarize(., lnMass = mean(lnMass), lnBMR = mean(lnBMR) + Ei/k*(mean(1/(temp+273.15)) - 1/T2)) %>% arrange(., species)

```

#### Make the full tree

```{r}
## Load in individual trees for each taxonomic group
amphib <- read.tree("../datasets/amph.tre")
birds <- read.tree("../datasets/bird.tre")
squam <- read.tree("../datasets/squa.tre")
mamm <- read.tree("../datasets/fullnewmammal.tre")
fish <- read.tree("../datasets/fish.tre")

## Make a taxonomy table:
trees <- list(fish=fish, amphib=amphib, squam=squam, birds=birds, mamm=mamm)
trees <- lapply(trees, function(x) reorder(x, "postorder"))
ntips <- sum(sapply(trees, function(x) length(x$tip.label)))
tip.labels <- c("fish", "amphib", "squam", "birds", "mamm")
classes <- lapply(1:length(c("fish", "amphibians", "squamates", "birds", "mammals")), function(x) data.frame("genspec"=trees[[x]]$tip.label, "class"=c("fish", "amphibians", "squamates", "birds", "mammals")[x]))
classes <- do.call(rbind, classes)
 
## Make a tree with just orders:
edge <- matrix(c(9, 4,
  9, 3,
  8, 5,
  8, 9,
  7, 8,
  7, 2,
  6, 7,
  6, 1), byrow=TRUE, ncol=2)
## Dates from Timetree of life (timetree.org)
edge.length <- c(274.9, 274.9, 324.5, 324.5-274.9, 382.9-324.5, 382.9, 454.6-382.9 , 454.6)
Nnode <- 4
ordertree <- list(edge=edge, Nnode=Nnode, tip.label=tip.labels, edge.length=edge.length)
class(ordertree) <- 'phylo'
ordertree <- reorder(ordertree, "postorder")
plot(ordertree)

## 
otax <- data.frame("Class"= ordertree$tip.label, "Superclass"=c("Actinopterygii", rep("Tetrapoda",4)))
rownames(otax) <- ordertree$tip.label
classtree <- nodelabel.phylo(ordertree, otax, ncores=1)
trees <- lapply(trees, multi2di)
class(trees) <- "multiPhylo"
plot(classtree)
#abline(v=sapply(trees, function(x) max(nodeHeights(x))),lty=2)
res <- glomogram.phylo(classtree, trees)
length(res$tip.label)
sum(res$edge.length)


#write.tree(res, file="../output/tetrapods.tre")
```


```{r}
vertTree <- read.tree("../datasets/tetrapods.tre")
length(vertTree$tip.label)
sum(vertTree$edge.length)
```

#### Use OpenTree of life taxonomic name resolution to find species in the dataset not found in the tree and see if the name has changed. Replace names in the data to match the tree. 

```{r}
missing <- setdiff(new.dat[[1]], vertTree$tip.label)
otl_missing <- ttol_queryOttIds(missing, nrequest=500, tree=FALSE)

clean.dat <- new.dat
clean.dat[[1]] <- as.character(clean.dat[[1]])
clean.dat[[1]][match(missing, new.dat[[1]])] <- otl_missing$ttol

## Manual changes to match tree:
clean.dat$species[clean.dat$species=="Urocitellus_townsendii"] <- "Urocitellus_townsendi"


```

#### Combine tree and data
```{r}
td <- make.treedata(vertTree, clean.dat)
```

#### Manual patches for erroneous data:
```{r}
patches <- read.csv("../datasets/BMR_corrected.csv")
patches2 <- read.csv("../datasets/BMR_corrected2.csv")
td$dat[match(patches2$taxon, td$phy$tip.label),] <- data.frame("lnMass"=log(patches2$newMass.g), "lnBMR"=patches2$NewRate.20)
drop <- patches$taxon[which(patches$action %in% c("cut"))]
td <- treeply(td, drop.tip, as.character(drop))

#saveRDS(td, "../output/data/tetrapods_ei.rds")
```

#### Re-Load in the final dataset.
```{r}
td <- readRDS("../output/data/tetrapods_ei.rds")
td
```

# Reversible-Jump Analyses

```{r}
source("./Manuscript_Models_dev.R")
```


```{r}
mod <- "RR000"
gens <- 1000000
prior <- priors[paste("prior", mod, sep=".")][[1]]
model <- models[paste("model", mod, sep=".")][[1]]
startpar <- startpars[paste("model", mod, sep=".")][[1]]


mymcmc <- bayou.makeMCMC(cache$phy, cache$dat, pred=cache$pred, SE=0, model=model, prior=prior, startpar=startpar, new.dir=TRUE, outname=paste(mod, "run1", sep="_"), plot.freq=NULL, ticker.freq=2000, samp = 200)
mymcmc$run(gens)

```


```{r}
chain <- mymcmc$load()
chain <- set.burnin(chain, 0.3)
plot(chain)
#pdf("deleteme.pdf", height=20, width=8)
plotSimmap.mcmc(chain, burnin=0.3, pp.cutoff=0.3, cex=0.25)
#dev.off()
```

```{r}
shiftsum <- shiftSummaries(chain, mymcmc, burnin=0.5, pp.cutoff=0.3)
#pdf("deleteme2.pdf")
plotShiftSummaries(shiftsum)
#dev.off()
```

```{r}
shiftsum$descendents
```



```{r}
rr <- c("_u001", "_u002", "_u003", "_u004", "_u005", "_u006")
chains.RR000 <- lapply(rr, function(x) readRDS(paste("../output/runs/tetrapods_ei/tetrapods_ei_", x, ".chain.rds", sep=""))) 
chains.RR000 <- combine.chains(chains.RR000, burnin.prop = 0.3)

```


